\chapter{Literature Review}

\todo{Reiterate research claims from Chapter 1 - Introduction.}

\noindent
\todo{Review literature around this claim from theoretical lenses.}

\section{Software Quality}

\todo[McCall's model was one of the first software quality models introduced. It described quality from X perspectives... this was further developed by the ISO quality model, which enhanced by Y... In the late 1990s, Dromey's interperation expanded...]{Background on the development of software quality models.}

\noindent
\todo{Relate software quality to CV systems; internal \& external quality.}

\noindent
\todo{Discuss gaps in the software quality literature relating directly to CV quality.}

\section{Probabilistic and Stochastic Systems}

\noindent
\todo{What are stochastic/probabilistic systems? E.g., model interpretation?}

\noindent
\todo{What understanding might be missing from model interpretation? Relate back to topic.}

\section{Cognitive Biases}

\noindent
\todo{Background; what are cognitive biases and how does it relate to SE?}

\noindent
\todo{Literature of CB specifically in SE.}

\noindent
\todo{List potential CBs with relation to the AI-based systems.}

\section{UX Consistency Principle}

\noindent
\todo{Background; what is UX consistency? What does it advocate for and why?}

\noindent
\todo{What lessons can we learn from UX consistency, and how can we apply it to SE?}

\noindent
\todo{What are the gaps in SE that do not conform to practices of UX consistency w.r.t. AI systems development?}

\section{API Documentation and Standards}

\noindent
\todo{What are API documentation standards? What do they advocate for?}

\noindent
\todo{What is missing for AI documentation? What is the gap?}

\section{Validation and Verification}

\noindent
\todo{Unsure...}

\section{Requirements Specification}

\noindent
\todo{Unsure...}

\section{Meta-modelling}

\noindent
\todo{What is meta-modelling? Can get this from honours thesis...?}

\noindent
\todo{How does this differ in AI context?}