\cleardoublepage
\pagestyle{empty}
\begin{center}
  \vspace*{0.3\paperheight}
  \textit{To my family, friends, and teachers.}
\end{center}
\pagestyle{fancy}

\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

\vspace{-2\bigskipamount}

A long journey of 20 years education has led me to this thesis, and there are so many people who've helped me get to this point that deserve thanking. To start, I must thank my family; you have always been there for me in times good and bad. I'm especially grateful to my mother, Rosa, my father, Paul, my siblings, Marc and Lisa, and my nonna, Michelina Bonacci, for your love and support. I also thank my nieces Nina and Lucy (though too young to read this now!) for bringing us all so much joy in these few years. I must thank all my teachers, particularly Natalie Heath from my time at Parade College, whose hard efforts certainly paid off in my tertiary education. And, of course, I thank all those who have helped shape this thesis. Firstly, to Professor Rajesh Vasa: thank you for your many revisions, patience, ideas, and efforts to shape this work. Your years of guidance---both as a supervisor and as a mentor---has reshaped my worldview I now approach thought and problem-solving in a remarkably new light. Secondly, I thank Professor John Grundy for being such an approachable and hard-working supervisor, always willing to provide structure, feedback, and guidance to help me get over the finish line. I also thank Dr Scott Barnett for the interest you have shown in my work and for the joint collaborations we achieved in the last two years. I thank Associate Professor Mohamed Abdelrazek for your many contributions within this thesis. Lastly, I thank Associate Professor Andrew Cain, who not only taught me the realm of programming back in undergraduate days, but who first suggested a PhD was within my reach which I'd never even fathomed. I must thank everyone at the Applied Artificial Intelligence Institute for creating such an enjoyable environment to work in, especially Jake Renzella,  Reuben Wilson, Dean Biddau, Beth Bland, Mahdi Babaei, Rodney Pilgrim, and Simon Vajda and for their friendship over these years and for all the coffee runs, conversations, and ideas shared. And, lastly, to Tom Fellowes: thank you for being by my side throughout this journey as we have worked to complete our PhDs together.

\bigskip
\noindent
This chapter is now over, the next chapter awaits...

\bigskip
\noindent
\hspace{\fill}
\parbox[b]{0.4\linewidth}{
\raggedleft
\small
--- \theauthor{}\\
\thedate{}
}

\chapter*{Statistics about this PhD}
\addcontentsline{toc}{chapter}{Statistics about this PhD}

This PhD journey consisted of the following:

\bigskip

\begin{itemize}
    \item 82,188 words;
    \item 38,281 lines of \LaTeX;
    \item 7 accepted publications;
    \item 3 rejected publications;
    \item 4 conferences, 2 attended virtually;
    \item 827 days of candidature;
    \item 3.7 months of examination;
    \item 1 global pandemic; and,
    \item 21 years of since my first day of primary school.
\end{itemize}

\bigskip


\epigraph{``...Now what?''}{--- Bloat, \textit{Finding Nemo} (2003)}