\newpage
\chapter*{Candidate Declaration}
\addcontentsline{toc}{chapter}{Candidate Declaration}

I certify that the thesis entitled ``\textit{\thetitle{}}'' submitted for the degree of \thedegree{} complies with all statements below.\bigskip
\begin{enumerate}[label=(\roman*)]
  \item I am the creator of all or part of the whole work(s) (including content and layout) and that where reference is made to the work of others, due acknowledgement is given.    
  \item The work(s) are not in any way a violation or infringement of any copyright, trademark, patent, or other rights whatsoever of any person.
  \item That if the work(s) have been commissioned, sponsored or supported by any organisation, I have fulfilled all of the obligations required by such contract or agreement.
  \item That any material in the thesis which has been accepted for a degree or diploma by any university or institution is identified in the text.
  \item All research integrity requirements have been complied with.
\end{enumerate}\bigskip
I certify that I am the student named below and that the information provided above is correct.

\vspace{2cm}

\noindent
\hspace{\fill}
\parbox[b]{0.4\linewidth}{
  \hrulefill\\
  \raggedleft
  \theauthor{}\\
  \footnotesize
  \thedate{}
}

\newpage
\chapter*{Access to Thesis}
\addcontentsline{toc}{chapter}{Access to Thesis}

I am the author of the thesis entitled ``\textit{\thetitle{}}'' submitted for the degree of \thedegree{}.

\bigskip
\noindent
This thesis may be made available for consultation, loan and limited copying in accordance with the \textit{Copyright Act 1968 (Cth)}.

\bigskip
\noindent
I certify that I am the student named below and that the information provided above is correct.

\vspace{2cm}

\noindent
\hspace{\fill}
\parbox[b]{0.4\linewidth}{
  \hrulefill\\
  \raggedleft
  \theauthor{}\\
  \footnotesize
  \thedate{}
}